mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-01-26 thesis/diff/0127_thesis.tex
update

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
In this paper, to improve the development efficiency, the mruby bytecode loader using Bluetooth is implemented as an extension of mruby on TECS.
In addition, multiple mruby programs run cooperatively in the proposed framework.
Experimental results demonstrates the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

{\bf Contribution}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
The proposed framework gives the contribution in the following points. 
\begin{enumerate}
\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
\ mruby bytecode loader using Bluetooth helps developers develop software.
Developers do not need to insert and pull out repeatedly and also to restart an OS.
Thus, the software development efficiency is improved.
\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
\ There is a probrem in multitasking of the current mruby on TECS.
It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking. 
In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
Developers can easily program multitasking.
Multitasked programing makes the range of software expand.
\end{enumerate}

@@

The 100,000 times loop program is used as mruby application for evaluation.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.

>>>>

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
In this paper, to improve the development efficiency, the mruby bytecode loader using Bluetooth is implemented as an extension of mruby on TECS.
In addition, multiple mruby programs run cooperatively in the proposed framework.
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

{\bf Contribution}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
The proposed framework gives the contribution in the following points. 
\begin{enumerate}
\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
\ mruby bytecode loader using Bluetooth helps developers develop software.
Developers do not need to insert and pull out a SD card repeatedly and also to restart an OS.
Thus, the software development efficiency is improved.
\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
\ There is a probrem in multitasking of the current mruby on TECS.
It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking. 
In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
Multitasked programing makes the range of software expand.
\end{enumerate}

@@

The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
